### 2019-07-09 README.rmd
fixes errors in README

Install and Setup
=================

@@

```{r}
install.packages("Rclean")
```

@@

```{r}
install.packages("devtools")
devtools::install_github("ProvTools/Rclean", ref = "dev")
```

@@

```{r}
library(Rclean)
```

@@

*Rclean* usage is simple. Have a script with code you want to clean
saved to disk. Then, just run the `clean` function with the path to
the script as the input:

```{r}
clean("./example/simple_script.R")
```

@@

```{r}
clean("./example/simple_script.R", "tab.15")
```

@@

```{r eval = FALSE}
my.code <- clean("./example/simple_script.R", "tab.15")
write.code(my.code, file = "x.R")
```

@@

So far, we've been using "prosepective" provenance generated from the
static code prior to execution. *Rclean* can also be used with
"retrospective" provenance, which is recorded during execution of a
script. Using it facilitates more accurate code cleaning, We can pass
the provenance to the `clean` function via `options`:

```{r eval = FALSE}
options(prov.json = readLines("prov_micro.json"))
```

@@

```{r eval = FALSE}
clean(rp = TRUE)

```

@@

```{r eval = FALSE}
clean(x, rp = TRUE)

```

@@

*Contributing*: if you would like to contribute, please read [[CONTRIBUTE.md]].

>>>>

Install
=======

@@

```{r eval = FALSE}
install.packages("Rclean")
```

@@

```{r eval = FALSE}
install.packages("devtools")
devtools::install_github("ProvTools/Rclean", ref = "dev")
```

@@

```{r eval = TRUE}
library(Rclean)
```

@@

*Rclean* usage is simple. Have a script with code you want to clean
saved to disk. Then, just run the `clean` function with the path to
the script as the input. Here, we can use an example script that is
included with the package:

```{r eval = TRUE}
clean("example/simple_script.R")
```

@@

```{r eval = TRUE}
clean("./example/simple_script.R", "tab.15")
```

@@

```{r eval = FALSE}
my.code <- clean("example/simple_script.R", "tab.15")
write.code(my.code, file = "x.R")
```

@@

So far, we've been using "prospective" provenance generated from the
static code prior to execution. *Rclean* can also be used with
"retrospective" provenance, which is recorded during execution of a
script. Using it facilitates more accurate code cleaning, We can pass
the provenance to the `clean` function via `options`:

```{r eval = TRUE}
options(prov.json = readLines("example/prov_micro.json"))
```

@@

```{r eval = TRUE}
clean(file = "example/micro.R", rp = TRUE)
```

@@

```{r eval = FALSE}
clean(file = "example/micro.R", var = "x", rp = TRUE)
```

@@
